### 2025-03-14 paper/sections/other/main_results.qmd
ok

using CTExperiments
using CTExperiments.CSV
using CTExperiments.DataFrames
using CTExperiments.StatsBase

@@

::: {.callout-note}

@fig-mnist shows much more plausible (faithful) counterfactuals for a model with CT than the model with conventional training (@fig-mnist-vanilla). In fact, this is not even using *ECCo+* and still showing better results than the best results we achieved in our AAAI paper for JEM ensembles.

![Counterfactual images for *MLP* with counterfactual training. The underlying generator, *ECCo*, aims to generate counterfactuals that are faithful to the model [@altmeyer2024faithful].](/paper/figures/mnist_mlp.png){#fig-mnist}

![Counterfactual images for *MLP* with conventional training. The underlying generator, *ECCo*, aims to generate counterfactuals that are faithful to the model [@altmeyer2024faithful].](/paper/figures/mnist_mlp_vanilla.png){#fig-mnist-vanilla}

>>>>

using CTExperiments
using CTExperiments.CSV
using CTExperiments.DataFrames
using CTExperiments.Plots
using CTExperiments.StatsBase
using Random

@@

Random.seed!(42)    # change seed for different outcome
overwrite = false   # set to `true` if you want to overwrite the file
fname = joinpath(res_dir,"mlp/mnist/grid_config.toml")
output_dir = mkpath("paper/experiments/output/extra/")
gen = CTExperiments.GeneratorParams(lambda_energy=25.0)
conv = "max_iter"
cfg = EvaluationConfig(
    grid_file=fname, 
    counterfactual_params=(conv=conv, generator_params=gen), 
    save_dir=output_dir,
    test_time=true
)
generate_factual_target_pairs(cfg; overwrite, nce=10)
plts = plot_ce(MNIST(), cfg; byvars="objective")
savefig(plts["objective"]["full"]["ecco"], "paper/figures/mnist_mlp.png")
savefig(plts["objective"]["vanilla"]["ecco"], "paper/figures/mnist_mlp_vanilla.png")
```

@fig-mnist shows much more plausible (faithful) counterfactuals for a model with CT than the model with conventional training (@fig-mnist-vanilla).

::: {layout="[10,-2,10]" layout-valign="top"}
![Counterfactual images for *MLP* with counterfactual training. Factual images are shown on the diagonal, with the corresponding counterfactual for each target class (columns) in that same row. The underlying generator, *ECCo*, aims to generate counterfactuals that are faithful to the model [@altmeyer2024faithful].](/paper/figures/mnist_mlp.png){#fig-mnist}

![The same setup, factuals, model architecture and generator as in @fig-mnist, but the model was trained with CT.](/paper/figures/mnist_mlp_vanilla.png){#fig-mnist-vanilla}
:::
